Brief Article

### 2012-02-11 power.tex
added figure for probability to pick dataplot versus size of lineup

For the distribution of $n_m$, the number of times out of $K$ that observers picked the last plot to show the most non-random structure, we get
\[
n_m\sim \left \{ 
\begin{array}{cl}
B_{K, (1-E[p_B])^{m-1} & \text { under } H_1\\
B_{K, 1/m} & \text { under } H_0
\end{array}
\right .
\]

>>>>

For the distribution of $n_m$, the number of times out of $K$ that observers picked the last plot to show the most non-random structure, we get
\[
n_m\sim \left \{ 
\begin{array}{cl}
B_{K, (1-E[p_B])^{m-1} & \text { under } H_1\\
B_{K, 1/m} & \text { under } H_0
\end{array}
\right .
\]
Figure \ref{power} gives an overview of the probability of picking the dataplot for lineups of different size (as $m$ increases we have an increased probability to observe a more highly structured nullplot by chance).
Even under $H_1$ we expect some observers to pick a nullplot with a probability that depends on the strength of the signal in our dataplot, i.e. reversely, we should be able to make use of the number of people who do not pick the dataplot in a lineup, to infer the strength of the signal of the dataplot.

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=2in]{images/powerplot.pdf} 
   \caption{Comparison of probabilities to pick the data plot for different size lineups $m$ and different values for data plot strength $p_B$. The grey line shows probability of picking the data plot under $H_0$.}
   \label{power}
\end{figure}
